Classless Java

### 2015-11-15 paper/sections/Implementation.tex
Minor changes to implementation section. I think it was already pretty good

Our implementation is based on extension to Lombok. In Eclipse, with an
interface annotated by \mixin, the automatic annotation processing is performed
and the information of the interface from compilation is captured in the
``Outline'' window, including all the methods inside the interface as well as
the generated ones. The custom transformation is easy and convenient to use.

The biggest reasons to use Lombok rather than using conventional Java annotation
processor are:
\begin{itemize}
\item Lombok is byte-code based instead of source-code based, which makes client
  code concise and easy to maintain. Such code generation is performed at
  compile time to modify bytecode. And during compile time, these methods are
  only generated in class files, with neither the source code modified nor new
  Java files generated.
\item Moreover, and probably more importantly, Lombok is capable of generating
  code \emph{inside} a class/interface.This is the ability that conventional
  Java annotation processor can not provide.
\end{itemize}

The implementation using Lombok has certain limitation: 
\begin{itemize}
\item Our implementation does not support separate compilation yet at this
  stage, for in the implementation it is hard to capture a type declaration from
  its reference.
\item At this stage our implementation only realizes the Eclipse handler and our
  experiments are all conducted in Eclipse.
\end{itemize}

>>>>

Our implementation is based on extension to Lombok. In Eclipse, with an
interface annotated by \mixin, the automatic annotation processing is performed
and the information of the interface from compilation is captured in the
``Outline'' window, including all the methods inside the interface as well as
the generated ones.
 The custom transformation is easy and convenient to use.
 For example this means that the IDE functionality 
 content assist autocomplete will work for the newly generated methods.

The biggest reasons to use Lombok rather than using conventional Java annotation
processor is
\begin{itemize}
%this seamd like a commercial spot
%\item Lombok is byte-code based instead of source-code based, which makes client
%  code concise and easy to maintain. Such code generation is performed at
%  compile time to modify bytecode.
\item Lombock modify the generation process of the class files.
neither the source code is modified nor new  Java files are generated.
\item Moreover, and probably more importantly, Lombok is capable of generating
  code \emph{inside} a class/interface.This is the ability that conventional
  Java annotation processor do not provide.
\end{itemize}

Our prototype implementation using Lombok has certain limitation: 
\begin{itemize}
\item We do not support separate compilation yet at this
  stage, for in the implementation it is hard to capture a type declaration from
  its reference.
\item At this stage our implementation only realizes the Eclipse handler and our experiments are all conducted in Eclipse.
\end{itemize}
